\documentclass{article}
\usepackage[margin=0.5in]{geometry}
\begin{document}

\title{\vspace{-2.0cm}Easy Desserts}
\author{Miquela Stein (with help from the internet)}
\maketitle{}
An easy way to make tasty chocolate desserts with very little effort! Great for parties or over-priced school bake sales.

\section{Chocolate Bark}
A delicious and easy treat that looks fancy with minimal effort! Makes $\sim$12 pieces of chocolate bark.
\subsection{Ingredients: General}
\begin{itemize}
\item 1 12-oz bag of chocolate chips (minimum)
\end{itemize}
Note: I usually get Nestle chocolate chips.
\subsection{Ingredients: Peppermint Bark}
\begin{itemize}
\item 1 12-oz bag of dark chocolate chips
\item 1 12-oz bag of white chocolate chips
\item 12 pieces of peppermint candy, crushed
\end{itemize}
\subsection{Ingredients: Salted Caramel Bark}
\begin{itemize}
\item 1 12-oz bag of white chocolate chips
\item 1 12-oz bag of butterscotch baking chips
\item Several pinches of sea salt
\item Caramel syrup topping
\end{itemize}

\subsection{Instructions}
Prep Time: 10-15 mins. Total Time: 1hr 10 mins - 1hr 15 mins.
\begin{itemize}
\item Cover cookie sheet with wax paper
\item Melt chocolate according to instructions on bag
\item Pour chocolate onto wax paper and spread until mostly smooth
\item For peppermint bark:
\begin{itemize}
\item Pour and smooth layer of white chocolate
\item Pour and smooth layer of dark chocolate on top
\item (Optional) Use a toothpick to create a simple marble look by drawing zig-zag lines in the chocolate
\item Sprinkle crushed peppermint candies over top layer while chocolate is hot
\end{itemize}
\item For salted caramel bark:
\begin{itemize}
\item Pour and smooth layer of white chocolate
\item Pour and smooth layer of butterscotch on top
\item Lightly sprinkle sea salt evenly across the chocolate while hot
\item Pour thin zig-zag lines of caramel over the chocolate while hot
\end{itemize}
\item Freeze chocolate for at least an hour, or until cold and solid
\item Remove the chocolate from the freezer and break into uneven pieces
\item Enjoy! Note: Keep frozen until eating time.
\end{itemize}

\section{Spheroidal Sweets}
More effort than chocolate bark, but still pretty easy! Makes $\sim$24-32 pieces, depending on size.
\subsection{Ingredients}
\begin{itemize}
\item 8 oz cream cheese
\item 16 oz cookies ($\sim$36 oreos; $\sim$32 nutter butters; $\sim$32 chips ahoy)
\item 1 12-oz bag of chocolate chips
\item (Optional) Mini cupcake holders
\end{itemize}

\subsection{Instructions}
Prep Time: 30-50 mins. Total time: 1 hr 30 mins - 1 hr 50 mins.
\begin{itemize}
\item Part 1 (The cookies):
\item Cover cookie sheet with wax paper
\item Crush and mix the cookies and cream cheese together in a gallon size plastic bag.
\begin{itemize}
\item Crunchy texture: Put cookies and cream cheese into bag and crush by hand.
\item Smooth texture: Blend cookies using a food processor, then pour cookie powder into bag and mix with cream cheese by hand.
\end{itemize}
\item Mix together in bag until (mostly) uniform consistency, and dough-like behavior.
\item Form $\sim$1in diameter spheres (or spheroids) from the mixture and place onto the wax paper until all mixture is used
\item Freeze for 1 hour, or until cold and solid
\item Part 2 (The chocolate):
\item Remove spheres from freezer
\item Prepare a place for the finished product
\begin{itemize}
\item Either cover another cookie sheet with wax paper
\item Or set up mini cupcake holders
\end{itemize}
\item Melt chocolate according to instructions on bag
\item Cover each spheroid in chocolate and place onto wax paper or cupcake holder
\item Freeze until chocolate is cold and solid
\item Enjoy! Note: Keep frozen until eating time.
\end{itemize}

\end{document}
